How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-03-30 tse-paper/content.tex
Add intro plan
drafts for data extraction section

% TODO: Include term predictive CI, link to FB paper and https://www-sciencedirect-com.tudelft.idm.oclc.org/science/article/pii/S0164121218301730
% TODO: What about the alternate solution, installing plugins to report precise data? Ie., maven plugins
% - Lots of effort
% - not a generic solution
% - how to analyze history where such plugins were not installed
% - unclear which information you want

@@

\subsection{Study Selection}

\Cref{fig:lit-survey} presents an overview of our study selection.
In this first literature overview study on analyzing build logs, we
therefore want to survey as broad a population of scientific material
as possible. Note that we do not limit our sources to specific
Software Engineering venues, as is often done, but survey all sources
monitored by Google Scholar, including Bachelor's and Master's theses,
academic slide decks, and books. We use Google Scholar as opposed to
Scopus or other databases, as it is the search engine for acdemic
articles with the broadest and most current index, including preprints
from sources such as arXiv. One challenge is that no common
nomenclature has been established yet (in fact, this is one of the
goals of this article).

Since we cannot take for granted that ``analyzing build logs'' is the
cannonical term that other, isolated works have used, we instead
decdided to leave out the potentially variable ``analysis'' part and
instead focus on variations of the term ``build log''. This has the
advantage of being biunique: We explicitly decided to exclude systems
or event logs (see \Cref{sec:rw}). On the other hand, a Google Scholar
search for ``build log'' returns more than 2.2 million results
(2020-03-15). We therefore refined our search criterions for the four
different spelling possibilities of ``build log'' to exclude obvious
non-related works. This left us with 1,552 combined search results
(2020-03-15).

@@

First, we filtered out articles based on 1) their title and 2) the
contextual information Google Scholar displayed. We inlcuded only
publications written in a language intelligible to the authors (that
is, English or German), but only disregarded fewer than 1\% of search
hits due to this criterion. Our strategy was to err on the side of
caution, that is rather including a paper than not. We then unified
the results of the four search queries based on the link as the
identifying element, removing 60 articles that appeared in more than
one search query. We noticed that some publishers (ACM, Springer,
Google Books) augment a link to an article with a cutomized ID, which
specifies the link source ({\tt casa\_token, oid}). We automatically
removed it to find all true duplicates. After this process, we were
left with 259 (17\%) of the original search results.

Wtih these 259 remaining articles, we followed a backward snowball
sampling for related work. This added three papers (five before
duplicate elimination) to our literature set, coming to a total of 261
articles.

On the 261 artciles, We did a second filter phase by downloading the
surviving papers, reading their abstracts, and searching the full text
for the occurrence of ``log''. If these papers showed even traces of
working with build logs, we included them in our survey. For the
snowballed set, we included two of the three articles, both of which
stem from the same first author, were borderline-includes, and had
called build logs from the Linux kernel ``build traces.'' In total, we
were left with 90 articles after this search.

\subsection{Article Classification}
%todo Caro: please write a draft for this :-)
Having trimmed down the set of articles, we investigated them in depth.

@@

\section{Future Work}

>>>>

% TODO: Introduction structure
% 0) we introduce & define the problem 1) we survey which techniques exist 2) we implement (for a lack of readily available implementations) and compare the most promising ones 3) we draw conclusions for when to use which technique

% TODO: Include term predictive CI, link to FB paper and https://www-sciencedirect-com.tudelft.idm.oclc.org/science/article/pii/S0164121218301730

% TODO: What about the alternate solution, installing plugins to report precise data? Ie., maven plugins
% - Lots of effort
% - not a generic solution
% - how to analyze history where such plugins were not installed
% - unclear which information you want

@@

\subsection{Study Selection}
% TODO shorten
\Cref{fig:lit-survey} presents an overview of our study selection.
In this first literature overview study on analyzing build logs, we
therefore want to survey as broad a population of scientific material
as possible. Note that we do not limit our sources to specific
Software Engineering venues, as is often done, but survey all sources
monitored by Google Scholar, including Bachelor's and Master's theses,
academic slide decks, and books. We use Google Scholar as opposed to
Scopus or other databases, as it is the search engine for acdemic
articles with the broadest and most current index, including preprints
from sources such as arXiv. One challenge is that no common
nomenclature has been established yet (in fact, this is one of the
goals of this article).

% TODO Caro cite guidelines
Since we cannot take for granted that ``analyzing build logs'' is the
cannonical term that other, isolated works have used, we instead
decdided to leave out the potentially variable ``analysis'' part and
instead focus on variations of the term ``build log''. This has the
advantage of being biunique: We explicitly decided to exclude systems
or event logs (see \Cref{sec:rw}). On the other hand, a Google Scholar
search for ``build log'' returns more than 2.2 million results
(2020-03-15). We therefore refined our search criterions for the four
different spelling possibilities of ``build log'' to exclude obvious
non-related works. This left us with 1,552 combined search results
(2020-03-15). The full search queries are documented in our replication
package \todo{cite/add replication package}.

@@

First, we filtered out articles based on 1) their title and 2) the
contextual information Google Scholar displayed. We inlcuded only
publications written in a language intelligible to the authors (that
is, English or German), but only disregarded fewer than 1\% of search
hits due to this criterion. Our strategy was to err on the side of
caution, that is rather including a paper than not. We then unified
the results of the four search queries based on the link as the
identifying element, removing 60 articles that appeared in more than
one search query. We noticed that some publishers (ACM, Springer,
Google Books) augment a link to an article with a cutomized ID, which
specifies the link source ({\tt casa\_token, oid}). \todo{overly specific?} We automatically
removed it to find all true duplicates. After this process, we were
left with 259 (17\%) of the original search results.

With these 259 remaining articles, we followed a backward snowball
sampling for related work. This added three papers (five before
duplicate elimination) to our literature set, coming to a total of 261
articles. % TODO Caro: update

On the surviving artciles, we did a second filter phase by downloading the
full articles, reading their abstracts, and searching the full text
for the occurrence of ``log''. If these papers showed traces of
working with build logs, we included them in our survey. For the
snowballed set, we included two of the three articles, both of which
stem from the same first author, were borderline-includes, and had
called build logs from the Linux kernel ``build traces.'' In total, we
were left with 90 articles after this search.

\subsection{Article Classification}
% TODO Caro: please write a draft for this :-)
Having trimmed down the set of articles, we investigated them in depth.
kept all articles that use logs from software builds as input to some kind of process.
we wanted to characterize how researchers use buildlogs as input to any processes.
Interesed in 
\begin{itemize}
  \item what kind of build logs they are using and the source of these logs.
  \item what information they are retrieving from the logs, 
  its kind (chunk/classification) and 
  what they use the retrieved information for
  \item which technique they are using to process the build logs,
  in how much detail it is described and whether they published their tools
\end{itemize}
To objecifiy our data extraction we created a template of the targeted factors
and performed a pilot on five articles. Two authors extracted the data from the
five pilot articles and we held a consensus meeting to unify our understanding
of the factors in the data extraction templates. The remaining articles were
divided over these two authors. We inspected the articles as closesly as necessary,
starting from occurences of ``log'' or ``build'' within the text.
The full data extraction template and our results of this step can be found in
our replication package \todo{cite}.

In this pass we further identified x duplicate articles \todo{do we push those to the last pass?}.
For several cases, multiple articles extended others, though still reported on
the same work with the respect to analyzing build logs.
Of these we only considered the earliest article which reported on the processing
of build logs.

\subsection{Results}
lots of:
- categories + frequencies of answers

\subsubsection{Retrieved Information}

\subsubsection{Retrieval Technique}

\subsubsection{Build Logs}

\subsection{Discussion}
various researchers analyzing build logs to support their research, tools developed
to help developers \todo{motivational reference}.

\subsubsection{Retrieved Information}
why from build logs? 
not avaliable in cleaner format
much use for research, a bit of developer information / tools
following: research so many logs that unfeasible to do manually, less focus on tools
for devs (caveat! we excluded books and documentation on industrial tools -> many
approaches there to make build logs digestible, tough many focus on general
minimizing of the data presented, not retrieving specific chunks)

\subsubsection{Retrieval Technique}
broadly mentioned shortly, rarely explained in detail
we follow that researchers often see this as an unimportant side fact
work needed to be done to get the big work done

\subsubsection{Build Logs}
often focussed on specific logs, sometimes mentioned because of effort developing a parser
other times also because other tools used in further research are limiting the scope
(reference paper with PIT tool).
many focus on maven because of it's prevalence also in respect to other tools
much research done on travis ci logs b/c of their abundance and open availability

@@

\section{Future Work}
\todo{survey build logs tools in industry}
